Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
midor edits
dissections of a quiver

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the orientable surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{itemize}
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v]$, $\Enrt{\alpha} = [v, t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual]$ and~$\Ert{\alpha} = [v\dual, t(\alpha)]$ (colored red) as follows:
\vincent{Figure}
\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\alpha)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{itemize}
The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
\end{definition}

@@

\begin{lemma}
\label{lem:walks=arcs}
Walks of~$\bar Q$ are precisely~$\dissection$ accordions.
\end{lemma}

>>>>

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v(\alpha)]$, $\Enrt{\alpha} = [v(\alpha), t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual(\alpha)]$ and~$\Ert{\alpha} = [v\dual(\alpha), t(\alpha)]$ (colored red) as follows:
\vincent{Figure}
\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\alpha)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{enumerate}
This defines an orientable surface~$\surface(\bar Q)$ with boundaries, endowed with two disjoint sets~$V_{\bar Q}$ and~$V\dual_{\bar Q}$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ defined as follows:
\begin{itemize}
\item $V_{\bar Q}$ is the set of points~$v(\alpha)$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii),
\item $\dissection_{\bar Q}$ is the $V_{\bar Q}$-dissection with one arc for each vertex~$p \in Q_0$ obtained by concataining the sides~$\Ert{\alpha} = \Ers{\beta}$ and~$\Ert{\alpha'} = \Ers{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \in I$ and~$\alpha'\beta' \in I$.
\item $V\dual_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ are defined dually.
\end{itemize}
\end{definition}

@@

\begin{lemma}
\label{lem:walks=arcs}
Walks of~$\bar Q$ are precisely~$\dissection$-accordions.
\end{lemma}
